paper_figs_rotations201911 : create paper figures from rotation runs

### 2019-11-27 inst/documents/paper_figs_rotations201911.Rmd
working on paper figs

---
title: "sensi_an_rotations201911. To analyse rotation runs for paper"
output: pdf_document
#output: word_document
author: "Andy South, Sam Jones and Ian Hastings"
date: "`r Sys.Date()`"
---

@@

Code below will need to be adapted to work on all 16 experiments, so far it just works on one.

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
  library(rotations)
  library(ggplot2)
  library(gridExtra)
  library(tidyverse)

@@

@@

#rot_minus_seq, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rot_minus_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-100,100) +
     xlab("advantage of rotations over sequence in generations") +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#rms (rot_minus_seq)_pcent, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rms_percent, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     scale_x_continuous(limits=c(-80,80), breaks = c(-60,-40,-20,0,20,40,60)) +
     xlab("percentage advantage of rotations over sequence in generations") +
     theme(panel.grid.minor=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#oooo this is interesting
#it shows what gens_rot the best strategies occur at
ggplot(df_res_16, aes(x=gens_rot, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("generations to reach thresholds for ROTATION") +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#gens_seq the best strategies occur at
ggplot(df_res_16, aes(x=gens_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("generations to reach thresholds for SEQUENCE") +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#Plots of how the difference between rotations and sequences respond to model inputs.

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5}

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5}

>>>>

---
title: "paper_figs_rotations201911 : create paper figures from rotation runs"
#output: pdf_document
output: word_document
author: "Andy South, Sam Jones and Ian Hastings"
date: "`r Sys.Date()`"
---

@@

```{r, eval=TRUE, include=FALSE}
#set to eval=TRUE to make figs for submission

library(knitr)

# options to create final publication quality figures
# word doc summarises & figs get stored
opts_chunk$set(dev="tiff",
               dev.args=list(compression="lzw"),
               dpi=300,
               cache=FALSE,
               fig.path='rotfigs/',
               fig.width=8.5,
               fig.height=8.5)
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
  library(rotations)
  library(ggplot2)
  library(gridExtra)
  library(tidyverse)
  library(patchwork) #for arranging multiple plots on page

@@

# example scenarios
# A1 frequency switch insecticides same, no costs no disp

```{r fig1-examp-run-A1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# TODO put into a reusable function to plot seq vs rot
# TODO probably allow run_rot to return the ggplot object

dfseq <- run_rot(rot_interval=0, n_insecticides=4, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=4, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE )

ggseq <- ggseq + theme(legend.position="none")
ggrot <- ggrot + theme(legend.position="bottom",
                       axis.title.y = element_blank())

#using patchwork
#plot seq and rot side-by-side
#guides=collect to put legend between plots, doesn't seem to work
(ggseq + ggrot) + plot_layout(guides = 'collect')

# A2 frequency switch insecticides same, costs no disp

```{r fig2-examp-run-A2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#TODO replace later, quick pasted test to see effect of adding cost

dfseq <- run_rot(rot_interval=0, n_insecticides=4, start_freqs=0.0026, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=4, start_freqs=0.0026, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE )

ggseq <- ggseq + theme(legend.position="none")
ggrot <- ggrot + theme(legend.position="bottom",
                       axis.title.y = element_blank())

#using patchwork
#plot seq and rot side-by-side
#guides=collect to put legend between plots, doesn't seem to work
(ggseq + ggrot) + plot_layout(guides = 'collect')

# A3 frequency switch insecticides same, no costs, disp
# in this example rotations have a reasonable advantage but I'm not sure why !!

```{r fig3-examp-run-A2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#TODO replace later, quick pasted test to see effect of adding dispersal

dfseq <- run_rot(rot_interval=0, n_insecticides=4, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=4, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE )

ggseq <- ggseq + theme(legend.position="none")
ggrot <- ggrot + theme(legend.position="bottom",
                       axis.title.y = element_blank())

#using patchwork
#plot seq and rot side-by-side
#guides=collect to put legend between plots, doesn't seem to work
(ggseq + ggrot) + plot_layout(guides = 'collect')

# B1 frequency switch insecticides different, no costs no disp

```{r fig4-examp-run-A1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

#rot_minus_seq, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rot_minus_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-100,100) +
     xlab("advantage of rotations over sequence in generations") +
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#rms (rot_minus_seq)_pcent, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rms_percent, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     scale_x_continuous(limits=c(-80,80), breaks = c(-60,-40,-20,0,20,40,60)) +
     xlab("percentage advantage of rotations over sequence in generations") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#oooo this is interesting
#it shows what gens_rot the best strategies occur at
ggplot(df_res_16, aes(x=gens_rot, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("generations to reach thresholds for ROTATION") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

#gens_seq the best strategies occur at
ggplot(df_res_16, aes(x=gens_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("generations to reach thresholds for SEQUENCE") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5}

# doesn't show much
# Plots of how the difference between rotations and sequences respond to model inputs.

@@

```{r figx-PRCC, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5}

@@

### 2019-11-27 inst/documents/rotations_notes.Rmd
working on paper figs

@@

Me :

@@

# TODO
see rotation_runs2019.Rmd & rotations-experiments-creating-201909.xlsx

1. find & fix problem with C runs see above
2. add change_interval as an input
3. should I set min_gens_switch_back and min_rwr_interval to 0, they should have no effect

>>>>

FIXED and new 16k simulations run.

@@

Me : (not sent)

@@

# 27/11/2019

paper_figs_rotations201911.Rmd

choose example runs for early figs

ARg, this may not matter,  but I had wondered if I could directly compare runs with and without costs.
BUT it seems the way that random samples are drawn that th values for other input change.

e.g. on p6, A1 no cost eff=0.79
A2 with cost cost=0.79, eff=0.99

run_rot(rot_interval=0, n_insecticides=5, start_freqs=0.092, cost=c(0), eff=c(0.79), dom_sel=c(0.16),
dom_cos=c(0.94), rr=c(0.19), expo_hi=0.73, male_expo_prop=0.15, coverage=1, migration=0,
min_rwr_interval=10)

run_rot(rot_interval=0, n_insecticides=5, start_freqs=0.077, cost=c(0.079), eff=c(0.99), dom_sel=c(0.5),
dom_cos=c(0.81), rr=c(0.38), expo_hi=0.46, male_expo_prop=0.16, coverage=1, migration=0,
change_interval=10)

This may not matter for the main runs. but may mean that I want to choose example runs differently.

Happens in set_run_inputs()

    # select random numbers for each insecticide
    cost <-     runif(n_rands, min=inex$cost_min,        max=inex$cost_max) 
    eff  <-     runif(n_rands, min=inex$eff_min,         max=inex$eff_max)

Interestingly, (and possibly worryingly) seems that the random deviate isn't used if min and max are the same.

# TODO

paper_figs_rotations201911.Rmd
see rotation_runs2019.Rmd & rotations-experiments-creating-201909.xlsx

a. create a function to compare seq and rot plots
1. check random number issues
2. look at paper3 folder
